TBD

### 2020-11-01 outputs/paper/paper.Rmd
model update

The model we use to predict the result of the election is MRP, multilevel regression with post-stratification. Logistic regression allows us the simplicity of analyzing the categorical response variable while incorporating both numerical and categorical explanatory variables; while combined with post-stratification it yields a prediction result closer to the population parameter.

We are interested in how variables such as age, education, race, family income, and geographic region affect citizens’ voting intentions. The response variable that we are interested in is the chances of a citizen voting for Trump in the coming presidential election. It is a categorical variable with two levels: 1 represents intending to vote for Donald Trump, and 2 means planning to vote for Joe Biden.

@@

where p is the probability of event A that we are interested in, $\beta_0$is the intercept, $x_1...x_K$ are our variables of interest and $\beta_1...\beta_k$ are parameters for each of these variables. Based on the result, we are able to estimate p for a particular case given all the variables.

The logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level. Then we come up with a weight for each stratum to adjust its influence towards our prediction. Namely, if a stratum is over-represented, we want to reduce its impact on the prediction result; if a stratum is under-represented, we want to increase its influence.
We need a post-stratification dataset that is large enough to do this. In this report, we use the ACS(reason).

@@

We find the mask parameter interesting, firstly because US is the country with the most COVID cases in the world, the influence of COVID on election choices is inevitable. Secondly, since Trump and Biden have very opposites towards the pandemic and how to handle it, this parameter will likely represent part of respondent's voting intention in the same way as any more common political indicators.

>>>>

The model we use to predict the result of the election is MRP, multilevel regression with post-stratification. The advantage of this model is that it has better performance when estimating behaviors of a particular subgroup of the population. One can interpret MRP as a combination of multilevel logistic regression and post-stratification. Logistic regression allows us the simplicity of analyzing the categorical response variable while incorporating both numerical and categorical explanatory variables; while combined with post-stratification it yields a much narrower confidence interval for the estimation.

We are interested in how variables such as age, education, race, family income, geographic region and mask wearing decision affect citizens’ voting intentions, particular between the major party candidates, Donald Trump for the Republicans and Joe Biden for the Democratic Party. The response variable that we are interested in is the chances of a citizen voting for Trump in the coming presidential election. It is a categorical variable with two levels: 1 represents intending to vote for Donald Trump, and 2 means planning to vote for Joe Biden.

Ideally, we ought to run a pre-analysis to determine the variables of interest. However due to the limited time and budget, we will leave that open for further analysis and for future elections. We chose the explanatory variables based on our understanding of the major characteristics of a respondent that could potentially affect a his/hers voting intention. Except for respondents' age, education, income level and state which are common in statistical studies, we are very interested in respondent's habits towards mask-wearing, firstly because US is the country with the most COVID cases in the world, the influence of COVID on the election votes is inevitable. Secondly, since Trump and Biden hold quite opposites opinions towards the handling of the pandemic, this parameter will likely represent part of respondent's voting intention in the same way as the more common political indicators.

@@

where p is the probability of event A that we are interested in, $\beta_0$is the intercept, $x_1...x_K$ are our variables of interest and $\beta_1...\beta_k$ are parameters for each of these variables. Based on the result, we are able to estimate p for a particular case given all the variables. We use `as.factors()` to incorporate dummy variables for all the categorical variable.

The main logic behind post-stratification is that we divide the sample data into strata based on a few attributes such as state, income, education level. Then we come up with a weight for each stratum to adjust its influence towards our prediction. Namely, if a stratum is over-represented, we want to reduce its impact on the prediction result; if a stratum is under-represented, we want to increase its influence. In this sense, the combination with logistic regression allows subgroups with a relatively low size to 'reference' from other subgroups with similar characteristics.

To mimic the population as closely as possible, we need a post-stratification dataset that is large enough to reference to. In this report, we use the ACS(reason).

@@
